{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
added citation "obversavtional determinism…"
added subsection for the conclusion
added whitespace

\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper\cite{Barthe07} which is as follows. After the introduction the basic
terms and definitions for a multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typable in this type system is secure w.r.t the notion of
security. The proof that this holds is sketched in the following section.
In the last section the (by now) abstract framework is instantiated with a
concrete example.

@@

\subsection{Observational Determinism for Concurrent Program Security}
\subsection{Flexible Scheduler-Independent Security\cite{Mantel10}}
This approach developed by Mantel and Sudbrock has the goal to be on the one hand
scheduler independent and on the other not too restrictive (i.e. does not treat
obviously secure programs as insecure).

@@

>>>>

\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper \cite{Barthe07} which is as follows. After the introduction the basic
terms and definitions for a multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typable in this type system is secure w.r.t the notion of
security. The proof that this holds is sketched in the following section.
In the last section the (by now) abstract framework is instantiated with a
concrete example.

@@

\subsection{Observational Determinism for Concurrent Program Security\cite{Zdancewic03}}
\subsection{Flexible Scheduler-Independent Security\cite{Mantel10}}
This approach developed by Mantel and Sudbrock has the goal to be on the one hand
scheduler independent and on the other not too restrictive (i.e. does not treat
obviously secure programs as insecure).

@@

\subsection{Conclusion}
